Printing in a Periphery: a Quantitative Study of Finnish Knowledge Production, 1640-1828

### 2016-07-14 inst/examples/20160715-slides-Krakow.Rmd
sync

**Customized** dedicated R packages for bibliographic analysis combine flexibility with automation

**Automated** scales well with new data and unforeseen changes; a million documents ~ 30 minutes

@@

# Pick the investigated period (sliding window)
# Sum up the years within this sliding window for each element    	    
dfw <- mapdata %>%
    	     group_by(publication_place, latitude, longitude, highlight, highlight2) %>%
		       summarize(n = sum(size))
dfw$size <- log10(1 + dfw$n)
dfw$size[!dfw$highlight2 == 1] <- max(dfw$size)

# Plot map
p <- ggmap(mymap) + 
      	geom_point(data = dfw,
      	  aes(
      	  x = longitude, 
      	  y = latitude,
	        size = size,
	        shape = highlight2, 
	        color = highlight)) +
	        ggtitle(i) +
	        scale_size(range = c(2, 15)) +
	        theme(title = element_text(size = 30), legend.position="none") +
	        scale_color_manual(values = c("black", "red")) +
	        scale_shape_manual(values = c(19,1))
print(p)
```

@@

# Title count per decade & publisher	
npub <- df %>% group_by(publication_decade, publisher) %>% tally() %>% arrange(n)
npub$publisher <- factor(npub$publisher, levels = (npub %>% group_by(publisher) %>% summarise(total = sum(n)) %>% arrange(total))$publisher)

>>>>

**Customized** our dedicated R packages for bibliographic analysis combine flexibility with automation

**Automated** scales well with new data and unforeseen changes; a million documents cleaned up in 30 minutes

@@

# Pick the investigated period (sliding window)
# Sum up the years within this sliding window for each element    	    
dfw <- mapdata %>%
    	     group_by(publication_place, latitude, longitude, highlight, highlight2) %>%
		       summarize(n = sum(size))
dfw$size <- log10(1 + dfw$n)
dfw$size[!dfw$highlight2 == 1] <- 0.5*max(dfw$size)

# Plot map
p <- ggmap(mymap) +

        	geom_point(data = subset(dfw, highlight2 == 1),
      	    aes(
      	      x = longitude, 
      	      y = latitude,
	            size = size,
	            shape = 1, 
	            #shape = highlight2, 
	            fill = highlight), 
      	      pch = 21, stroke = 1) +

        	geom_point(data = subset(dfw, !highlight2 == 1),
      	    aes(
      	      thickness = 10,
      	      x = longitude, 
      	      y = latitude,
	            shape = 19, 
	            #shape = highlight2, 
	            color = highlight), 
      	      colour = "black", 
      	      shape = 21, # Point shape 
      	      size = 7,   # Point size
      	      stroke = 2) + # Point edge thickness

	        ggtitle(i) +
	        scale_size(range = c(2, 15)) +
	        theme(title = element_text(size = 30), legend.position="none") +
	        scale_fill_manual(values = c("darkgray", "red")) #+
	        #scale_shape_manual(values = c(19,1))
print(p)
```

@@

# Title count per decade & publisher	
npub <- df %>% group_by(publication_decade, publisher) %>% tally() %>% arrange(n)
#npub$publisher <- factor(npub$publisher, levels = (npub %>% group_by(publisher) %>% summarise(total = sum(n)) %>% arrange(total))$publisher)
# Sort by biggest publication decade
#ord <- (npub %>% group_by(publisher) %>% summarise(decade = publication_decade[[which.max(n)]]) %>% arrange(decade))$publisher
ord <- as.character((npub %>% group_by(publisher) %>% 
                        summarise(decade = median(publication_decade)) %>% 
                        arrange(decade))$publisher)
npub$publisher <- factor(npub$publisher, levels = ord)
